A Novel Model-Free Actor-Critic Reinforcement Learning Approach for Dynamic Target Tracking

### 2020-07-03 paperMIC2020/paperIEEE-MIC2020-V1.tex
Latex file is updated and merged
fixed issues

\title{A Novel Model-Free Learning Approach for Dynamic Target Tracking Problem and its Validation using Virtual Robot Experimentation Platform 
%  
% \thanks{This work was supported in part by the Bradley University’s Caterpillar fellowship grant.}
}

@@

\begin{IEEEkeywords}
Leader-follower formation, mobile robots, reinforcement learning, policy iteration, trajectory tracking
\end{IEEEkeywords}

@@

\section{Introduction}
\label{sec:introduction}
\todo[inline]{Need to discuss in details the limitations of previous work, we
  can also add RL applications to robotics navigation}

Tracking a random moving target using a mobile robot, for instance, is a challenging task. This is mainly due to their inherent complex nonlinear dynamics. Most of the target tracking algorithms proposed in the literature either rely on A) complex mathematical models, B) simplified mathematical models, and C) nonlinear control techniques or driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity.

Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks to name a few \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001}.  In all of these mentioned applications a fleet of robot i.e agents interact with each other to achieve a certain goal. Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's promising applications in research and industry. In a typical target tracking formation a number of robots referred to as followers apply local control actions to follow a target in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} many control methods were proposed however they have had the following limitations:
\\(1) a static leader/target is used.
\\(2) the leade/target's location or dynamic model is predetermined.  
\\(3) expensive hardware platforms are used to achieve the mobile target tracking.

The main contribution of this work is the development of a model-free learning approach to control the follower robot by which it overcome many of the limitations mentiond above as it does not rely on any prior information of the mathmetical model or the dynamic model. The steering angle and the linear speed of the follower robot are determined by collecting the position and orientation of both the leader and the follower. This set of information is gathered online over a finite period of time. The optimal control actions are then generated by utilizing Bellman's principal of optimality which acts as model free-reinfocment learning approach that allows the follower robot to follow the path of the leader while avoiding collision by maintaining a safe distance. In this paper the proposed algorithm is further validated using a commercially available robot simulator, CoppeliaSim. This paper acts as first milestone in generalizing the algorithm to solve more sophisticated problem such as coverage and mapping. \hl{cite area coverage papers}  
The rest of the paper is orgnized as follows. Section II lays down the problem setting of the leader follower problem and mathemetical models of the robots and the state error. The model free actor-critic reinforcment learning and its key steps are described in section III.Section IV illustrates computer simulations for different secnarios that reflects the effectivness of the proposed method followed by conlusion and future work presented in section V.

@@

Fig.~\ref{fig:leaderFollowerSetup} shows the setup of the problem that we address in this manuscript. The robot is characterized by its 2D position $(x_k,y_k)$ and orientation $\theta_k\in[-\pi,\pi)$ with respect to global coordinate frame X-Y at discrete time index $k=0,1,\ldots,$ where time $t=kT$ with $T>0$ being the sampling time. The time-varying position of the target is denoted by ${\bf p}_k^{[d]}= [x_k^{[d]},y_k^{[d]}]^T\in\mathbb{R}^2.$  Let the position and orientation (pose) of the robot is denoted by the vector  ${\bf q}_k^T\equiv[x_k,y_k,\theta_k]\in\mathbb{R}^2\times\mathbb{S}^1.$ Without loss of generality, assume that the robot tracks the target's trajectory while maintaining line-of-sight distance (also known as safe distance between the robot and the target) $d>0.$ We emphasize that the mathematical models of both robot and the target are not required in the proposed control technology. For illustration, let us assume that the robot (rear-wheel drive) follows the discrete-time kinematic model described by %
%
\begin{subequations}
  \begin{align}
    \label{eq:robotModelDT}
    x_{k+1} &= x_k +T\nu_k\cos\theta_k\\
    y_{k+1} &= y_k +T\nu_k\sin\theta_k\\
    \theta_{k+1} &= \theta_k + T\frac{\nu_k}{L}\tan\gamma_k
  \end{align}
\end{subequations}
%
where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the steering angle of the font castor of the robot (see Fig.~\ref{fig:leaderFollowerSetup}), and $\nu_k\in\mathbb{R}$ is the linear speed. Without loss of generality, this work considers a target modeled by an integrator and its discrete-time kinematic model is described by 
 \begin{align}
   \label{eq:leaderDT}
   \mathbf{p}_{k+1}^{[d]} = \mathbf{p}_k^{[d]} + T_s \, \mathbf{u}_k^{[d]},
 \end{align}  
with $\mathbf{u}_k^{[d]}\in\mathbb{R}^2$ being the control input vector (velocity) that defines the trajectory (considered random in this work) of the target.  In case, the robot modeled by~\eqref{eq:robotModelDT} is described by a differential drive mobile robot, then its left-wheel velocity $\nu_{L,k}$ and right-wheel velocity $(\nu_{R,k})$ are related as 
  \begin{figure}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/ipe/LFMICSetup.eps}
    }
   \caption{Mobile robot and its dynamic target tracking problem setup.}
   \label{fig:leaderFollowerSetup}
 \end{figure}
 \begin{subequations}
   \begin{align}
     \nu_{k} &= \frac{1}{2}(\nu_{R,k} + \nu_{L,k}),\\
     \omega_{k} &= \frac{1}{\ell}(\nu_{R,k} - \nu_{L,k}) = \frac{\nu_{k}}{L}\tan(\gamma_k) 	
   \end{align}
 \label{eq:robotModel1-DT}
 \end{subequations}
 %
 where $\omega_k = \frac{\nu_k}{L}\tan\gamma_k$ is the angular velocity of the robot's center $(x_k,y_k).$ Let us define the error vector as 
 \begin{align}
     \label{eq:stateError}
   \mathbf{e}_k = [\rho_k,\tilde\theta_k]^T=[\sqrt{\tilde{x}_k^2+\tilde{y}_k^2},\tilde{\theta_k}]^T% = \\
   % \begin{bmatrix}
   %   \sqrt{(x_k^{[d]} - x_k - d\cos\theta_k^{'})^2+
   %   (y_k^{[d]} - y_k - d\sin\theta_k^{'})^2},
   %   \theta_k^{'} - \theta_k
   % \end{bmatrix},
 \end{align}
% 
 where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right)$
 and ${\rho_k} =\sqrt{\tilde{x}_k^2+\tilde{y}_k^2} $ is the Euclidean distance at time instant $k$ as shown in Fig.~\ref{fig:leaderFollowerSetup} with $\tilde{x}_k = x_k^{[d]} - x_k - d\cos\theta_k^{'},$ $\tilde{y}_k = y_k^{[d]} - y_k - d\sin\theta_k^{'},$ and $\tilde{\theta}_k = \theta_k^{'} - \theta_k.$ The control problem can then be formally stated as follows: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:robotModelDT}~and~\eqref{eq:leaderDT}.

@@

 \begin{multline*}
   \delta_c =\sum_{\kappa=0}^{\eta-1}\frac{1}{2}\varepsilon_{k+\kappa}^2=\sum_{\kappa=0}^{\eta-1}\frac{1}{2}(\boldsymbol{\omega}^T\tilde{\bm{\rho}}(\mathbf{z}_{k+\kappa,k+\kappa+1})-{v}_{k+\kappa})^2 = \frac{1}{2}\| \mathbf{v} - \bm{\Lambda}\bm{\omega}\|^2\\
   =\frac{1}{2}\left(\mathbf{v} - \bm{\Lambda}\bm{\omega}\right)^T \left(\mathbf{v} - \bm{\Lambda}\bm{\omega}\right), 
 \end{multline*}

@@

   \bm{\omega}_c^{[r+1]} = \bm{\omega}_c^{[r]} - \ell_c\frac{\partial\delta_c}{\partial \bm{\omega}} = \bm{\omega}_c^{[r]} - \ell_c\left(-\bm{\Lambda}^T\mathbf{v} + \bm{\Lambda}^T \bm{\Lambda}\bm{\omega}_c^{[r]}\right)\\ 

@@

 \begin{center}
 ${\bf P}=\begin{bmatrix} 
 2\,\omega^{[1]}    & \omega^{[2]}      & \omega^{[3]}       & \omega^{[4]}        \\ 
 \omega^{[2]}       &2\, \omega^{[5]}   & \omega^{[6]}       & \omega^{[7]}        \\
 \omega^{[3]}       & \omega^{[6]}      &2\, \omega^{[8]}   & \omega^{[9]}   \\   
 \omega^{[4]}       & \omega^{[7]}      & \omega^{[9]}      & 2\,\omega^{[10]}      
 \end{bmatrix}\in \mathbb{R}^{4\times 4},$
 \end{center}
 %
 where $\omega^{[i]}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}_c.$

@@

        \foreach \l [count=\i] in {1,2}
        \draw [<-] (input-\i) -- ++(-1,0)
        node [above, midway] {$\mathbf{e}_{k,\l}$};

        \foreach \l [count=\i] in {1,2,\mbox{$n^{'}$}}
        \node [above] at (hidden-\i.north) {$\sigma_{\l}$};

@@

                 Solve for the critic-weights $\bm{\omega_c}$ using~\eqref{eq:criticWeights}eights}\;
                 Solve for the actor-weights $\bm{\omega_a}$ using ~\eqref{eq:actorWeights}\;\;

@@

@@

 \section{Computer Experiments and Results}
 \label{sec:resultsExperiments}
 \todo[inline]{review}
 This section adopts the theoritical results discussed in the previous section by simulating the Algorithm using the Pioneer 3-DX  robot. The proposed Actor-Critic RL algorithm is tested using the commercial robot simulator CoppeliaSim in integration with Matlab software as a prelminary step to implement the Algorithm experimantally in real world.Here we present the performance of the proposed method and the convergence characterisitcs of the actor and critic weights. The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.001,0.001]$ and $\mathbf{R} = \mathrm{diag}[10^{-5}, 10^{-5}].$ % 
  \[Q=0.001 
  \begin{bmatrix}
  1       & 0   \\
  0       & 1   \\
  \end{bmatrix},
  R=0.00001
  \begin{bmatrix}
  1       & 0 \\
  0       & 1 
  \end{bmatrix}.\]

 The actor and critic learning rates $\ell_c$,$\ell_a$ are set to  $0.0001$ and $0.01$ respectively. The sampling time $T_s$ is set to $0.001 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.2$ [m].

  During the simulation CoppeliaSim simulator accuratly mimics what would happen in a realworld scenario following idustry standatrds and guidlines.The setup of the virtual expirement is illustrated  in figure \ref{fig:CoppeliaSim Scene} where pioneer robot model was initally placed at position $(x,y) = (-1,-2.5) $ [m] with an orientation $\theta = 0 \degree$ .The Target which is modeled as a cylinder object was initially located at a random position around  $(x,y) = (0,0)$ [m]. The simulation was run for the duration of 15 seconds. 
  The Target is set to move on a completely random trajectory starting from a random position. We intensify that the follower robot has no previous knoweledge of the dynamic model of the moving target nor it's initial position. The results obtained by the simulation are shown in figure \ref{fig:simulationResults}. the control actions of the pioneer robot are determined by the random actor weights .we clearly see tracking error converges to the desired value of $d$ = 0.2 [m] along with control signal converging to values that allows target tracking. the results reveal the ability of the proposed algorithm to sucessfully track the dynamic moving target and adapt to the changes in the target's path in an online manner.      
\begin{figure}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/coppeliasim.png}
`     }
   \caption{Simulation Setup}
   \label{fig:CoppeliaSim Scene}
 \end{figure}

@@

 \section{Conclusion} \label{sec:conclusion}
	\todo[inline]{review}
	A model free actor-critic reinfoncement learning algorithm for dynamic target tracking has been validated using virtual robot experimantation platform where a differenitial drive mobile robot and a randomly moving target are utilized in the simulation.Opposed to previous approaches in the litrature this Algorithm possess the advantage of being completlety model free and doesn't rely on any dynamic model to be known in priori. The actor weights which drives the control actions of the robot sucessfully converge to values that enable the robot to track the moving target through unplanned trajectory. To the authors knowlege this work is the first of its kind to employ a model-free actor-critic RL approach  in the context of dynamic target tracking. In future work the proposed approach will be applied to multi-robot scenarios where a number of robots are to achieve a certain task in unknown enviroments.

	\bibliographystyle{IEEEtran}
\bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
\end{document}

>>>>

\title{A Novel Model-Free Actor-Critic  Reinforcement Learning Approach for Dynamic Target Tracking  
%  
% \thanks{This work was supported in part by the Bradley University’s Caterpillar fellowship grant.}
}

@@

\begin{IEEEkeywords}
target tracking, mobile robots, reinforcement learning, policy iteration, trajectory tracking
\end{IEEEkeywords}

@@

\section{Introduction}
\label{sec:introduction}

Tracking a random moving target using a mobile robot is a key problem and a fundemental feature in Autonomus robots in areas such as survillance,search and rescure missions, enviromental monitoring and household cleaning to name a few \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001},\cite{Kitowski2012},\cite{Zhang2013}. Throught the years dynamic target tracking problem has recieved profound amount of research in academia and industry.  This is mainly due to their inherent complex nonlinear dynamics. Most of the target tracking algorithms proposed in the literature either rely on A) mathematical and kinematic models of both the robot and the target \cite{Huang2008}, B) the assumption that the target or it's path are static and known in prior, and C) nonlinear control techniques or driven by large amount of mostly offline data that leads to an overwhelming degree of computational complexity \cite{KD2007},\cite{Cren2017}. In a typical tracking problem a robot is to apply a local control actions that enables the robot to maintain a relative position and orientation from the designated target while following a certain path.It can also be applied on a fleet of robots where multiple robots mainatin a geometric configuration relative to the target\cite{Oh2015-Survey},\cite{Liu2017-Modular}.

%Tracking a random moving target using a mobile robot, for instance, is a challenging task.

%Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks to name a few .  In all of these mentioned applications a fleet of robot i.e agents interact with each other to achieve a certain goal. Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's promising applications in research and industry. In a typical target tracking formation a number of robots referred to as followers apply local control actions to follow a target in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.}

Reinforcement learning (RL) is an emerging field of machine learning which refers to a set of algorithms and techniques in which agent learn by interacting with the enviroment and generates it's own set of data. Reinorcement learning has long been applied on games and simulated enviroments but it has recently extended to robots in real world applications such as localization and mapping,area coverage, path planning and obstacle avoidance \cite{kober2013reinforcement},\cite{smart2002},\cite{michels2005},\cite{adekunle2016}.

In this paper we develop a model-free actor-critic learning  approach to control a non-holonomic wheeled mobile robot.The proposed method offers many advantages over other methods mentioned in the litreature such as being completely model free and does not require any knowledge of the mathemtaical model of the robot or the moving target and without the need for large computational power. The steering angle and the linear speed of the robot referred to as the policy are determined by collecting the position and orientation of both the target and the robot. This set of information is gathered online over a finite period of time. The optimal control actions are then generated by utilizing Bellman's principal of optimality which acts as model free-reinfocment learning approach that allows the  robot to follow the path of the target while avoiding collision by maintaining a safe distance. Here we extend the work proposed by authors in \cite{miah2020} by incorporating actor neural network along with critic network to find optimal control policy for the trajectory tracking problem. This work acts as first milestone in generalizing the algorithm to solve more sophisticated problem such as coverage and mapping.

The rest of the paper is orgnized as follows. Section II lays down the problem setting of the dynamic target tracking problem and mathemetical models of the robot and the state error. The model free actor-critic reinforcment learning algorithm and all the mathemetical equations are detailed in section III.Section IV illustrates computer simulations for different secnarios that reflects the effectivness of the proposed method followed by conlusion and future work presented in section V.

@@

Fig.~\ref{fig:leaderFollowerSetup} shows the setup of the problem that we address in this manuscript. The robot is characterized by its 2D position $(x_k,y_k)$ and orientation $\theta_k\in[-\pi,\pi)$ with respect to global coordinate frame X-Y at discrete time index $k=0,1,\ldots,$ where time $t=kT$ with $T>0$ being the sampling time. The time-varying position of the target is denoted by ${\bf p}_k^{[d]}= [x_k^{[d]},y_k^{[d]}]^T\in\mathbb{R}^2.$  Let the position and orientation (pose) of the robot is denoted by the vector  ${\bf q}_k^T\equiv[x_k,y_k,\theta_k]\in\mathbb{R}^2\times\mathbb{S}^1.$ Without loss of generality, assume that the robot tracks the target's trajectory while maintaining line-of-sight distance (also known as safe distance between the robot and the target) $d>0.$ We emphasize that the mathematical models of both robot and the target are not required in the proposed control technology. For illustration, let us assume that the robot (rear-wheel drive) follows the discrete-time kinematic model described by %
%
\begin{subequations}
  \begin{align}
    \label{eq:robotModelDT}
    x_{k+1} &= x_k +T\nu_k\cos\theta_k\\
    y_{k+1} &= y_k +T\nu_k\sin\theta_k\\
    \theta_{k+1} &= \theta_k + T\frac{\nu_k}{L}\tan\gamma_k
  \end{align}
\end{subequations}
%
where $\gamma_k\in(-\frac{\pi}{2},\frac{\pi}{2})$ is the steering angle of the font castor of the robot (see Fig.~\ref{fig:leaderFollowerSetup}), and $\nu_k\in\mathbb{R}$ is the linear speed. Without loss of generality, this work considers a target modeled by an integrator and its discrete-time kinematic model is described by 
 \begin{align}
   \label{eq:leaderDT}
   \mathbf{p}_{k+1}^{[d]} = \mathbf{p}_k^{[d]} + T_s \, \mathbf{u}_k^{[d]},
 \end{align}  
with $\mathbf{u}_k^{[d]}\in\mathbb{R}^2$ being the control input vector (velocity) that defines the trajectory (considered random in this work) of the target.  In case, the robot modeled by~\eqref{eq:robotModelDT} is described by a differential drive mobile robot, then its left-wheel velocity $\nu_{L,k}$ and right-wheel velocity $(\nu_{R,k})$ are related as 
  \begin{figure}
   \centering
   \fcolorbox{gray!10}{gray!5}{
     \includegraphics[width=0.45\textwidth]{figs/ipe/LFMICSetup.eps}
    }
   \caption{Mobile robot and its dynamic target tracking problem setup.}
   \label{fig:leaderFollowerSetup}
 \end{figure}
 \begin{subequations}
   \begin{align}
     \nu_{k} &= \frac{1}{2}(\nu_{R,k} + \nu_{L,k}),\\
     \omega_{k} &= \frac{1}{\ell}(\nu_{R,k} - \nu_{L,k}) = \frac{\nu_{k}}{L}\tan(\gamma_k) 	
   \end{align}
 \label{eq:robotModel1-DT}
 \end{subequations}
 %
 where $\omega_k = \frac{\nu_k}{L}\tan\gamma_k$ is the angular velocity of the robot's center $(x_k,y_k).$ Let us define the error vector as 
 \begin{align}
     \label{eq:stateError}
   \mathbf{e}_k = [\tilde{\rho_k},\tilde\theta_k]^T=[\sqrt{\tilde{x}_k^2+\tilde{y}_k^2},\tilde{\theta_k}]^T% = \\
   % \begin{bmatrix}
   %   \sqrt{(x_k^{[d]} - x_k - d\cos\theta_k^{'})^2+
   %   (y_k^{[d]} - y_k - d\sin\theta_k^{'})^2},
   %   \theta_k^{'} - \theta_k
   % \end{bmatrix},
 \end{align}
% 
 where $\theta_k^{'} = \mathrm{atan2}\left(y_k^{[d]}-y_k, x_k^{[d]}-x_k\right)$
 and ${\rho_k} =\sqrt{\tilde{x}_k^2+\tilde{y}_k^2} $ is the Euclidean distance at time instant $k$ as shown in Fig.~\ref{fig:leaderFollowerSetup} with $\tilde{x}_k = x_k^{[d]} - x_k - d\cos\theta_k^{'},$ $\tilde{y}_k = y_k^{[d]} - y_k - d\sin\theta_k^{'},$ and $\tilde{\theta}_k = \theta_k^{'} - \theta_k.$ The control problem can then be formally stated as follows: Find $\nu_k$ and $\gamma_k$ such that ${\bf e}_k\to {\bf 0}$ as  $k\to\infty$ subject to~\eqref{eq:robotModelDT}~and~\eqref{eq:leaderDT}.

@@

   \delta_c =\sum_{\kappa=0}^{\eta-1}\frac{1}{2}\varepsilon_{k+\kappa}^2 &=\sum_{\kappa=0}^{\eta-1}\frac{1}{2}(\boldsymbol{\omega_c}^T\tilde{\bm{\rho}}(\mathbf{z}_{k+\kappa,k+\kappa+1})-{v}_{k+\kappa})^2 \nonumber \\        	
   	&=\frac{1}{2}\| \mathbf{v} - \bm{\Lambda}\bm{\omega_c}\|^2 \nonumber \\
   &=\frac{1}{2}\left(\mathbf{v} - \bm{\Lambda}\bm{\omega_c}\right)^T \left(\mathbf{v} - \bm{\Lambda}\bm{\omega_c}\right), 

@@

   \bm{\omega}_c^{[r+1]} = \bm{\omega}_c^{[r]} - \ell_c\frac{\partial\delta_c}{\partial \bm{\omega_c}} = \bm{\omega}_c^{[r]} - \ell_c\left(-\bm{\Lambda}^T\mathbf{v} + \bm{\Lambda}^T \bm{\Lambda}\bm{\omega}_c^{[r]}\right)\\ 

@@

 \begin{center}
 ${\bf P}=\begin{bmatrix} 
 2\,\omega_c^{[1]}    & \omega_c^{[2]}      & \omega_c^{[3]}       & \omega_c^{[4]}        \\ 
 \omega_c^{[2]}       &2\, \omega_c^{[5]}   & \omega_c^{[6]}       & \omega_c^{[7]}        \\
 \omega_c^{[3]}       & \omega_c^{[6]}      &2\, \omega_c^{[8]}   & \omega_c^{[9]}   \\   
 \omega_c^{[4]}       & \omega_c^{[7]}      & \omega_c^{[9]}      & 2\,\omega_c^{[10]}      
 \end{bmatrix}\in \mathbb{R}^{4\times 4},$
 \end{center}
 %
 where $\omega^{[i]}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}_c.$

@@

        \foreach \l [count=\i] in {1}
        \draw [<-] (input-\i) -- ++(-1,0)
        node [above, midway] {$\mathbf{e}_{k,1}=\tilde{\rho_{k}}$};
		\draw [<-] (input-2) -- ++(-1,0)
        node [above, midway] {$\mathbf{e}_{k,2}=\tilde{\theta_{k}}$};
        \foreach \l [count=\i] in {1,2,\mbox{$n^{'}$}}
        \node [above] at (hidden-\i.north) {$\sigma_{\l}$};

@@

                 Solve for the critic-weights $\bm{\omega_c}$ using~\eqref{eq:criticWeights}\;
                 Solve for the actor-weights $\bm{\omega_a}$ using ~\eqref{eq:actorWeights}\;

@@

             }}

@@

 \section{Computer Experiments and Results}
 \label{sec:resultsExperiments}

 This section adopts the theoritical results discussed in the previous section by simulating the Algorithm using a differential drive mobile robot. The proposed Actor-Critic RL algorithm is tested  utilizing Matlab software and Robot Operating system (ROS)  as a prelminary step to implement the Algorithm experimantally in real world.Here we present the performance of the proposed method and the convergence characterisitcs of the actor and critic weights. The weighting matrices are set to $\mathbf{Q} = \mathrm{diag}[0.001,0.001]$ and $\mathbf{R} = \mathrm{diag}[10^{-5}, 10^{-5}].$ % 
  \[Q=0.001 
  \begin{bmatrix}
  1       & 0   \\
  0       & 1   \\
  \end{bmatrix},
  R=0.00001
  \begin{bmatrix}
  1       & 0 \\
  0       & 1 
  \end{bmatrix}.\]

 The actor and critic learning rates $\ell_c$,$\ell_a$ are set to  $0.0001$ and $0.01$ respectively. The sampling time $T_s$ is set to $0.001 \sec.$ The desired distance offset between the leader and the follower is set to $ d = 0.2$ [m] for the first scenario and $d = 0.5$ [m] for the second.

   In the first scenario the differential drive robot was initally placed at position $(x^d,y^d) = (-1,-5) $ [m] with an orientation $\theta = 0 \degree$ .The Target which is modeled as a cylinder object was initially located at a random position around  $(x,y) = (0,0)$ [m]. The simulation was run for the duration of 60 seconds.The targer is set to move following a sinusoidal path modeled as  $
 x^{[d]}(t) = \alpha (t) \in [0,10\pi], %
 y^{[d]}(t) = 5 \,\sin(\alpha t),$  and %
 $\theta^{[d]}(t) = cos(\alpha t).  %
$ In the begining of the simulation the robot starts to move away from the target according to the intial random actor weights.As the robot collects more information the robot adjust the control actions as the actor and critic weights started to converge and the robot asymptotically follows the target's trajectory.

  In the second scenario the Target is set to move on a completely random trajectory starting from a random position around $(x^[d],y^[d])=(1,5)$ with 
 $\dot x^{[d]}(t) = \nu^{[d]}(t)\cos\theta^{[\ell]}(t),$ %
 $\dot y^{[d]}(t) = \nu^{[d]}(t)\sin\theta^{[\ell]}(t).$
$ \dot\theta^{[d]}(t) = \omega(t)$,
 where $\nu^{[d]}(t)=0.2$ [m]. The robot intial position and orientation being $(x,y) = (0,0)$. We intensify that the robot has no previous knoweledge of the dynamic model of the moving target nor it's initial position. The results obtained by the simulation are shown in figure \ref{fig:simulationResults}. the control actions of the robot are determined by the random actor weights .we clearly see tracking error converges and approaches zero as the control signal converging to values that allows target tracking. the results reveal the ability of the proposed algorithm to sucessfully track the dynamic moving target and adapt to the changes in the target's trajectory and learns online by trial and error in different scenarios.      
%\begin{figure}
%   \centering
%   \fcolorbox{gray!10}{gray!5}{
%     \includegraphics[width=0.45\textwidth]{figs/coppeliasim.png}
%`     }
%   \caption{Simulation Setup}
%   \label{fig:CoppeliaSim Scene}
% \end{figure}  
 \begin{figure*}[htbp]%

 \subfigure[][]{%
    \label{fig:trajectoryRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/trajectoryRandomPathDistance.eps} }
	\subfigure[][]{%    
    \label{fig:euclideanDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/euclideanDistance.eps} }
\subfigure[][]{%
    \label{fig:stateErrorRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/stateErrorRandomPathDistance.eps} }
 \subfigure[][]{%
    \label{fig:controlInputsRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/controlInputRandomPathDistance.eps} }
 \subfigure[][]{%
    \label{fig:weightRandomDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightRandomPathDistance.eps} }
     \subfigure[][]{%
    \label{fig:actorWeightRandomDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/secondScenario/weightActor.eps} }
\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
  \label{fig:peformanceRandomTrajectory}%
	\label{fig:simulationResults}
\end{figure*}

@@

 \section{Conclusion} \label{sec:conclusion}

	A model free actor-critic reinfoncement learning algorithm for dynamic target tracking has been validated using set of computer simulation where a differenitial drive mobile robot and a randomly moving target are utilized in the simulation.Opposed to previous approaches in the litrature this Algorithm possess the advantage of being completlety model free and doesn't rely on any dynamic model to be known in priori. The actor weights which drives the control actions of the robot sucessfully converge to values that enable the robot to asymptotically track the moving target through unplanned trajectory. To the authors knowlege this work is the first of its kind to employ a model-free actor-critic RL approach  in the context of dynamic target tracking. In future work the proposed approach will be applied to multi-robot scenarios where a number of robots are to achieve a certain task in unknown enviroments.

	\bibliographystyle{IEEEtran}
\bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar,bib/amrsRefs}
\end{document}
